Repeatability Test

### 2017-08-19 pt_characterization/rep_check/u_s_time.tex
New 3D plot

\section{Further Investigation of the Existing Runs and Some Additional Runs~\label{sec:u_s_time_hist}} 
This section exhibits user and system time histograms on the first run of 
INC with its task length increasing from 1 second to 1024 seconds 
and the second run of INC from 2048 seconds to 16384 seconds via EMPv5 with no Step 2.
The detailed description of the base data is from Table~\ref{tab:exp_notes1}, 
and for some additional data, the corresponding description is given in Table~\ref{tab:exp_notes4}.

@@

\subsection{Summary of Histograms}

\begin{figure}[htp!]
\vspace{-.3in}
	\centering
	\includegraphics[scale=0.6,angle=270]{u_s_time/3d_plot.eps}\label{fig:3d_plot}
	\caption{3D histograms on INC~\label{fig:hist3d}}
\end{figure}

@@

\subsection{Absolute and Relative Variance over Increasing Task Length}

\begin{figure}[htp!]
	\centering
	\subfigure[Standard deviation (absolute)]{
		%\includegraphics[scale=0.6]{u_s_time/overall_std.eps}
		\includegraphics[scale=0.6]{u_s_time/new_overall_pt_std.eps}
		\label{fig:overall_std}
	}
	\subfigure[Standard deviation (absolute) in log scale]{
		%\includegraphics[scale=0.6]{u_s_time/overall_std_log.eps}
		\includegraphics[scale=0.6]{u_s_time/new_overall_pt_std_log.eps}
		\label{fig:overall_std_log}
	}
	\subfigure[Coefficient of variation in log scale (relative)]{
		\includegraphics[scale=0.6]{u_s_time/overall_re.eps}
		\label{fig:overall_re}
	}
	\subfigure[Coefficient of variation in log scale (relative): divisor=task length]{
		\includegraphics[scale=0.6]{u_s_time/new_overall_pt_re.eps}
		\label{fig:overall_re2}
	}
	\caption{Absolute and relative variances~\label{fig:cv_inc}}
\end{figure}

>>>>

\section{Further Investigation of the Existing Runs and Some Additional Runs~\label{sec:u_s_time_hist}} 
This section exhibits user and system time histograms on the first run of 
INC with its task length increasing from 1 second to 4096 seconds 
and the second run of INC from 8192 seconds to 16384 seconds via EMPv5 with no Step 2.
The detailed description of the base data is from Table~\ref{tab:exp_notes1}, 
and for some additional data, the corresponding description is given in Table~\ref{tab:exp_notes4}.

@@

\subsection{Summary of Histograms}
Figure~\ref{fig:hist3d} represents a 3D plot of collecting 
the selected histograms from the first and second runs: 
Figures ~\ref{fig:s9_r1_pt_hist1},~\ref{fig:s9_r1_pt_hist2},~\ref{fig:s9_r1_pt_hist3}, and ~\ref{fig:s9_r1_pt_hist4} (associated with INC1$\sim$INC4096 of the first run) and~\ref{fig:inc8192_r2_hist_v5} and~\ref{fig:inc16384_r2_hist_v5} (associated with  INC8192$\sim$INC16384 of the second run). The x-, y-, z-axes 
indicate bins (PT range), task length, 
and relative frequency of each histogram.

\begin{figure}[htp!]
\vspace{-.3in}
	\centering
	%\includegraphics[scale=0.6,angle=270]{u_s_time/3d_plot.eps}\label{fig:3d_plot}
	\includegraphics[scale=0.6]{u_s_time/new_3d_plot}\label{fig:3d_plot}
	\caption{3D histograms on INC~\label{fig:hist3d}}
\end{figure}

@@

\subsection{Absolute and Relative Variance over Increasing Task Lengths}
Figure~\ref{fig:cv_inc} exhibits absolute and relative variances over increasing task lengths. 
More specifically, Figures~\ref{fig:overall_std} and~\ref{fig:overall_std_log} 
concern the PT standard deviations on INC1$\sim$INC4096 of the first run and 
INC8192$\sim$INC16384 on the second run, as well as those from 
the intermediate task lengths described in Table~\ref{tab:exp_notes4}. 
The y-axis in Figure~\ref{fig:overall_std_log} is taken in log scale.
Figures~\ref{fig:overall_re} and~\ref{fig:overall_re2} shows 
the relative variance of the same data set---{\em coefficient of variation} (= standard deviation 
/ task length or mean). Both the x and y axes in these two figures are taken in log scale.

\begin{figure}[htp!]
	\centering
	\subfigure[Standard deviation (absolute)]{
		%\includegraphics[scale=0.6]{u_s_time/overall_std.eps}
		\includegraphics[scale=0.6]{u_s_time/new_overall_pt_std.eps}
		\label{fig:overall_std}
	}
	\subfigure[Standard deviation (absolute) in log scale]{
		%\includegraphics[scale=0.6]{u_s_time/overall_std_log.eps}
		\includegraphics[scale=0.6]{u_s_time/new_overall_pt_std_log.eps}
		\label{fig:overall_std_log}
	}
	\subfigure[Coefficient of variation in log scale (relative): divisor=mean]{
		\includegraphics[scale=0.6]{u_s_time/overall_re.eps}
		\label{fig:overall_re}
	}
	\subfigure[Coefficient of variation in log scale (relative): divisor=task length]{
		\includegraphics[scale=0.6]{u_s_time/new_overall_pt_re.eps}
		\label{fig:overall_re2}
	}
	\caption{Absolute and relative variances~\label{fig:cv_inc}}
\end{figure}
